UKB Models

### 2023-10-23 ukb_curation-eda.Rmd
testing additional permutations of sim.site groupings

>>>>

## Simulate Sites - Permutations

# Create a list to store data frames
df_list <- list()

for(i in 1:5) {
  new_col_name <- paste0("SimSite", i)
  # Separate samples for males and females
  sampled_males <- sample(sim.site.list, size = n_male, replace = TRUE, prob = male_prob)
  sampled_females <- sample(sim.site.list, size = n_female, replace = TRUE, prob = female_prob)

  new_df <- ukb_df_age.filt %>%
    mutate(!!new_col_name := as.factor(ifelse(sex == "Male", sampled_males, sampled_females)))%>%
    dplyr::select(!!new_col_name)

  # Store the data frame in the list
  df_list[[i]] <- new_df
}

# Combine data frames into a single data frame
ukb_df_sites_perm <- bind_cols(ukb_df_age.filt, !!!df_list)

# View the final dataframe
print(ukb_df_sites_perm)
#names(ukb_df_sites_perm)
```
```{r}
sim.perm.long <- ukb_df_sites_perm %>%
  dplyr::select(sex, age_days, contains("SimSite")) %>%
  pivot_longer(!c(sex, age_days), names_to = "permutation", names_prefix = "SimSite", values_to = "site")

prop <- sim.perm.long %>%
  group_by(permutation, site, sex) %>%
  summarize(Count = n(), avg_age = mean(age_days)) %>%
  group_by(permutation, site) %>%
  mutate(Proportion = Count / sum(Count))

summary.prop.male <- prop %>%
  dplyr::filter(sex=="Male") %>%
  group_by(site) %>%
  summarize(avg_prop = mean(Proportion), min_prop = min(Proportion), max_prop = max(Proportion))

summary.prop.male <- prop %>%
  group_by(site, sex) %>%
  summarize(avg_age_days = mean(avg_age), min_age = min(avg_age), max_age = max(avg_age))
```

```{r}
#write out
write_csv(ukb_df_sites_perm, file="data/ukb_CN_data_simsites_perm.csv")
```
